Watch Out for the Bully! Study of Interference Between Jobs Running Concurrently on Dragonfly Network

### 2016-03-07 draft.tex
add section synthetic trace analysis

% \begin{figure*}[t!]
%   \centering
%   \includegraphics[height=2.2in]{data_amount}
%   \caption{Applications data transfer amount}
%   \label{fig:3app-data-amount}
% \end{figure*}

@@

The amount of transferring data of each application are shown in Figure \ref{fig:3app-data-amount}.

@@

Figure \ref{fig:wkld-network-traffic} and Figure \ref{fig:global-channel-stime} shows that random job placement with adaptive routing can distribute workload traffic and balance the load over the network. Contiguous job placement

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/commtime}
        \caption{AMG Communication Time}
        \label{fig:amg-commtime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{mg/commtime}
        \caption{MG Communication Time}
        \label{fig:mg-commtime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{cr/commtime}
        \caption{CR Communication Time}
        \label{fig:cr-commtime}
    \end{subfigure}%
   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement and routing configurations. Random job placement and adaptive routing can improve MG and CR communication, however, AMG's communication time is greatly prolonged.}
   \label{fig:apps-commtime}
\end{figure*}

@@

We look into network level to identify the major culprit behind AMG's abnormal behavior with random placement and adaptive routing. By identifying the terminal nodes and routers that each application's traffic go through, we can see that the traffic amount go through the routers that belongs to AMG is skyrocketing when it running with random placement and adaptive routing, shown in Figure \ref{fig:amg-router-traffic}.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/tl-traffic}
        \caption{Terminal Link Traffic}
        \label{fig:amg-tl-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/lc-traffic}
        \caption{Local Channel Traffic}
        \label{fig:amg-lc-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/gc-traffic}
        \caption{Global Channel Traffic}
        \label{fig:amg-gc-traffic}
    \end{subfigure}%
   \caption{AMG router traffic.}
   \label{fig:amg-router-traffic}
\end{figure*}

Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG.

>>>>

@@

% The amount of transferring data of each application are shown in Figure \ref{fig:3app-data-amount}.

@@

Figure \ref{fig:wkld-network-traffic} and Figure \ref{fig:wkld-network-stime} shows that random job placement with adaptive routing can distribute workload traffic and balance the load over the network. Contiguous job placement

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{amg/commtime}
        \caption{AMG Communication Time}
        \label{fig:amg-commtime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{mg/commtime}
        \caption{MG Communication Time}
        \label{fig:mg-commtime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{cr/commtime}
        \caption{CR Communication Time}
        \label{fig:cr-commtime}
    \end{subfigure}%
   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement and routing configurations. Random job placement and adaptive routing can improve MG and CR communication, however, AMG's communication time is greatly prolonged.}
   \label{fig:apps-commtime}
\end{figure*}

@@

We look into network level to identify the major culprit behind AMG's abnormal behavior with random placement and adaptive routing. By identifying the terminal nodes and routers that each application's traffic go through, we can see that the traffic amount go through the routers that belongs to AMG is skyrocketing when it running with random placement and adaptive routing, shown in Figure \ref{fig:amg-lc-traffic} and Figure \ref{fig:amg-gc-traffic}. Adaptive routing will redirect the traffic of other applications to go through the routers belongs to AMG, and increase the burden of those routers, thus slow down the communication of AMG.

CrystalRouter and MultiGrid can get obvious benefit from random placement and adaptive routing, as we can see from Figure \ref{fig:cr-gc-traffic} \ref{fig:cr-lc-traffic} and Figure \ref{fig:mg-gc-traffic} \ref{fig:mg-lc-traffic}, random placement and adaptive routing can redirect their traffic to other region of network, to avoid local congestion as appeared with contiguous and minimal routing.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/lc-traffic}
        \caption{AMG Local Channel Traffic}
        \label{fig:amg-lc-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{mg/lc-traffic}
        \caption{MG Local Channel Traffic}
        \label{fig:mg-lc-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{cr/lc-traffic}
        \caption{CR Local Channel Traffic}
        \label{fig:cr-lc-traffic}
    \end{subfigure}%
   \caption{Each Application Router Local Channel Traffic.  }
   \label{fig:3app-lc-traffic}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{amg/gc-traffic}
        \caption{AMG Global Channel Traffic}
        \label{fig:amg-gc-traffic}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{mg/gc-traffic}
        \caption{MG Global Channel Traffic}
        \label{fig:mg-gc-traffic}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.8 in]{cr/gc-traffic}
        \caption{CR Global Channel Traffic}
        \label{fig:cr-gc-traffic}
    \end{subfigure}%
   \caption{Each Application Router Global Channel Traffic.}
   \label{fig:3app-gl-traffic}
\end{figure*}

Why AMG is the only victim in the workload? The reason for CrystalRouter and MultiGrid get improvement in the sacrifice of AMG's performance is that AMG is the lest communication-intensive application in the workload. As shown in Figure \ref{fig:3app-data-amount}, AMG has the least amount of data transfer between its ranks.

\begin{figure*}[t!]
  \centering
  \includegraphics[height=2.2in]{data_amount}
  \caption{Applications Data Transfer Amount. AMG has the least amount of data transfer, compared with CR and MG.}
  \label{fig:3app-data-amount}
\end{figure*}

Apparently, random placement and adaptive routing is quite efficient for orchestrate the traffic load in the network. Random placement and adaptive routing can uniformly distribute the workload traffic all over the network, make the load-balanced and avoid hot-spots. However, application like AMG will be impaired in this orchestration. The routers through which the less communication-intensive application traffic used to route, now have more traffic go through them. These extra traffic are from other communication-intensive applications. Beneath the facade of harmony, less communication-intensive application are bullied by their communication-intensive peers in the workload.

\section{Analysis of Synthetic Workloads}

To validate our assumption, we generate synthetic application, sAMG, which are same the with AMG's original traces in every aspect expect that the data transfer amount 100x greater than AMG.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/amg10/commtime}
        \caption{sAMG Communication Time}
        \label{fig:amg-commtime}
    \end{subfigure}%
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/mg/commtime}
        \caption{MG Communication Time}
        \label{fig:mg-commtime}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.5 in]{syn-wkld/cr/commtime}
        \caption{CR Communication Time}
        \label{fig:cr-commtime}
    \end{subfigure}%
   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement and routing configurations. Random placement and adaptive routing can improves AMG's communication time. MG and CR communication time are prolonged with random placement and adaptive routing.}
   \label{fig:apps-commtime}
\end{figure*}
